Avoidance in permutations

### 2014-11-07 project2/paper/paper.tex
FIxed label

In Sections \ref{S3} and \ref{S4} we consider sequences $s_n(\pi)$ for $\pi$ a permutation on the set $\{1,2,3\}$, and prove that the sequence $s_n(\pi)$ for all such $\pi$ is in fact the sequence of Catalan numbers. In Section \ref{S4} we will consider sequences $s_n(\pi)$ for $\pi$ a permutation of $\{1,2,3,4\}$. In Section \ref{Tn} we consider a variation of the avoidance problem that considers the problem of avoiding sequences in a subset $T_n$ of the permutations of $n$ elements. Before proceeding, however, we formally introduce the notation that will be used throughout this paper.

@@

\section{Terms in the sequence $s_n(321)$}

>>>>

In Sections \ref{S3} and \ref{S32} we consider sequences $s_n(\pi)$ for $\pi$ a permutation on the set $\{1,2,3\}$, and prove that the sequence $s_n(\pi)$ for all such $\pi$ is in fact the sequence of Catalan numbers. In Section \ref{S4} we will consider sequences $s_n(\pi)$ for $\pi$ a permutation of $\{1,2,3,4\}$. In Section \ref{Tn} we consider a variation of the avoidance problem that considers the problem of avoiding sequences in a subset $T_n$ of the permutations of $n$ elements. Before proceeding, however, we formally introduce the notation that will be used throughout this paper.

@@

\section{Terms in the sequence $s_n(321)$}
\label{S32}
